A demonstration of the \LaTeXe\ class file for \itshape{\journalnamelc}\footnotemark[2]

### 2019-09-30 journal/abstract.tex
more on fuzzgoat and SCB

Measuring the distance between two program executions is a fundamental problem in dynamic analysis of software, and useful in many test generation and debugging algorithms.  This paper proposes a metric for measuring distance between executions, and specializes it to an important application: determining similarity of failing test cases for the purpose of automated fault identification and localization in debugging based on automatically generated compiler tests.  The metric is based on a causal concept of distance where executions are similar to the degree that changes in the program itself, introduced by mutation, cause similar changes in the correctness of the executions.  Specifically, if two failing test cases for a compiler can be made to pass by applying the same mutant, those two tests are more likely to be due to the same fault.  We evaluate our metric using more than 50 faults and 2,800 test cases for two widely-used real-world compilers, and demonstrate improvements over state-of-the-art methods for fault identification and localization.  A simple operator-selection approach to reducing the number of mutants can reduce the cost of our approach by 70\%, while producing a gain in fault identification accuracy.  We additionally show that our approach, though devised for compilers, is applicable as a conservative fault localization algorithm for other types of programs.

>>>>

Measuring the distance between two program executions is a fundamental problem in dynamic analysis of software, and useful in many test generation and debugging algorithms.  This paper proposes a metric for measuring distance between executions, and specializes it to an important application: determining similarity of failing test cases for the purpose of automated fault identification and localization in debugging based on automatically generated compiler tests.  The metric is based on a causal concept of distance where executions are similar to the degree that changes in the program itself, introduced by mutation, cause similar changes in the correctness of the executions.  Specifically, if two failing test cases for a compiler can be made to pass by applying the same mutant, those two tests are more likely to be due to the same fault.  We evaluate our metric using more than 50 faults and 2,800 test cases for two widely-used real-world compilers, and demonstrate improvements over state-of-the-art methods for fault identification and localization.  A simple operator-selection approach to reducing the number of mutants can reduce the cost of our approach by 70\%, while producing a gain in fault identification accuracy.  We additionally show that our approach, though devised for compilers, is applicable as a conservative fault localization algorithm for other types of programs, and can help triage certain types of crashes found in fuzzing non-compiler programs more effectively than a state-of-the-art technique.

### 2019-09-30 journal/conclusions.tex
more on fuzzgoat and SCB

>>>>

Finally, the results of our comparison with semantic crash bucketing
(SCB) \cite{SCB},
which we consider the state-of-the-art in general-purpose fuzzer
taming, suggest what may be the most important line of future work.
When SCB applies to a set of crashes, it is cheap, effective, and
provides a useful bucketing.  However, it is very hard to imagine the
manual-patch template approach of SCB ever applying to complex compiler
bugs, or even to all the kinds of faults that might be found in
fuzzing of other targets, as discussed in Secton \ref{fuzzgoat}.  We
believe, however, that a
combination of SCB with our FPF-and-mutant-repair approach, perhaps using operator
selection to approximate a large, imprecise, set of ``patch
templates,'' and using semantic guidance to select among these, might offer a fuzzer taming method that is both
extremely practical (like SCB) but also truly general-purpose (like
our mutation-based approach).  In Section \ref{fuzzgoat} we propose a
simple two-phase approach, using SCB first, then our approach, but we
believe a more principled combination of the methods might provide
truly effective fuzzer taming, at a reasonable cost.

### 2019-09-30 journal/experiments.tex
more on fuzzgoat and SCB

\section{Experimental Results}

@@

\subsection{Discussion}

@@

\section{Fuzzer Taming for A Non-Compiler Target: Fuzzgoat}

%\subsection{Fuzzgoat}

@@

  These crashes exhibit a classic fuzzer taming structure.  Three of the bugs are easy to identify: they are triggered by 15, 14, and 11 of the 38 AFL-produced crashing inputs, respectively, and all have multiple inputs that uniquely detect that bug, and no other.  The fourth bug, however, is only triggered by \emph{three} of the 38 inputs, and is never uniquely present (any input triggering it also triggers at least one other bug).  The bug frees a pointer that can subsequently be used, and it is (as often with use-after-frees \cite{DangSan}) hard to produce inputs that actually cause this to happen. This bug was only found by AFL after nearly an hour of fuzzing, in fact.

@@

To our knowledge, the state-of-the-art in research on advancing fuzzing triage over the tools built into fuzzers like AFL is represented by the \emph{semantic crash bucketing} (SCB) approach of van Tonder, Kotheimer, and Le Goues \cite{SCB}.  This approach uses patch templates based on common types of bugs/semi-fixes, combined with semantic information obtained by observing the execution of a crashing input, to bucket crashing inputs discovered by fuzzers.  We contacted the SCB authors, and with their cooperation investigated how well SCB handled the fuzzgoat crashes.  The fuzzgoat code highlights the primary limitation of SCB: namely, if a kind of failure is not handled by a (manually constructed) patch template and identified by the semantic feedback mechanisms, then SCB does not really handle it.  The SCB tool was able to produce a patch for one of the four fuzzgoat bugs, a null pointer dereference.  Unfortunately, at present, SCB does not handle bugs related to misuse of {\tt free} (use-after-free, double frees, or frees of invalid pointers), and the other three fuzzgoat bugs are all {\tt free}-related.  SCB therefore can very effectively identify the inputs associated with one of the four bugs (when it is the only one triggeered by the input), but provides no assistance with finding the other three bugs. This is not to say that SCB is useless here; the null pointer bug alone is responsible for 13 of the 38 crashes, so SCB does make it easy to see one example of the null pointer bug, and ignore another 12 inputs.  It does not, however, help find the rare bug with only a few instances among the remaining 25 inputs.  While mutation repair also has no knowledge of {\tt free} bugs, it is able to find mutants that avoid their symptoms or their causes, and thus triage all four faults effectively.   The SCB team added the fuzzgoat example to their published VM, and plan to use it to drive development of patch templates and analysis for use-after-frees; this will, at some point, likely make it possible for SCB to handle fuzzgoat effectively.  However, in the long term, if fuzzing is applied to find assertion violations, differential testing divergences \cite{Differential,ICSEDiff}, or other more complex ``custom'' properties, as is likely with the appearance of tools such as DeepState \cite{DeepState} that merge fuzzing and property-based testing, it is hard to see how SCB will handle these ``custom'' bug types.

@@

>>>>

\section{Core Experimental Results: Compiler Triage and Debugging}

@@

\section{Discussion}

@@

\section{Fuzzer Taming for A Non-Compiler Target: Fuzzgoat}
\label{fuzzgoat}
%\subsection{Fuzzgoat}

@@

  These crashes exhibit the usual fuzzer taming structure, where some bugs are far more frequently found than others.  Three of the bugs are easy to identify: they are triggered by 15, 14, and 11 of the 38 AFL-produced crashing inputs, respectively, and all have multiple inputs that uniquely detect that bug, and no other.  The fourth bug, however, is only triggered by \emph{three} of the 38 inputs, and is never uniquely present (any input triggering it also triggers at least one other bug).  The bug frees a pointer that can subsequently be used, and it is (as often with use-after-frees \cite{DangSan}) hard to produce inputs that actually cause this to happen. This bug was only found by AFL after nearly an hour of fuzzing, in fact.

@@

To our knowledge, the state-of-the-art in research on advancing fuzzing triage over the tools built into fuzzers like AFL is represented by the \emph{semantic crash bucketing} (SCB) approach of van Tonder, Kotheimer, and Le Goues \cite{SCB}.  This approach uses patch templates based on common types of bugs/semi-fixes, combined with semantic information obtained by observing the execution of a crashing input, to bucket crashing inputs discovered by fuzzers.  We contacted the SCB authors, and with their cooperation investigated how well SCB handled the fuzzgoat crashes.  The fuzzgoat code highlights the primary limitation of SCB: namely, if a kind of failure is not handled by a (manually constructed) patch template and identified by the semantic feedback mechanisms, then SCB does not really handle it.  The SCB tool was able to produce a patch for one of the four fuzzgoat bugs, a null pointer dereference.  Unfortunately, at present, SCB does not handle bugs related to misuse of {\tt free} (use-after-free, double frees, or frees of invalid pointers), and the other three fuzzgoat bugs are all {\tt free}-related.  SCB therefore can very effectively identify the inputs associated with one of the four bugs (when it is the only one triggeered by the input), but provides no assistance with finding the other three bugs. This is not to say that SCB is useless here; the null pointer bug is responsible for 15 of the 38 crashes, so SCB does make it easy to see an instance of the null pointer bug, and ignore 14 additional inputs.  It does not, however, help find the rare bug with only a few instances among the remaining 23 inputs.  While mutation repair also has no knowledge of {\tt free} bugs, it is able to find mutants that avoid their symptoms or their causes, and thus triage all four faults effectively.   The SCB team added the fuzzgoat example to their published VM, and plan to use it to drive development of patch templates and analysis for use-after-frees; this will, at some point, likely make it possible for SCB to handle fuzzgoat effectively.  However, in the long term, if fuzzing is applied to find assertion violations, differential testing divergences \cite{Differential,ICSEDiff}, or other more complex ``custom'' properties, as is likely with the appearance of tools such as DeepState \cite{DeepState} that merge fuzzing and property-based testing, it is hard to see how SCB will handle these ``custom'' bug types.

@@

Unsurprisingly, the repairing-mutants approach does not improve on SCB on the set of bugs from the SCB paper \cite{SCB}.  These bugs were intentionally selected to consist of null pointers and buffer overflows; SCB in this setting operates as a bucketing version of repair that only has to use a selected, known-relevant set of mutants.  Repair is good at ranking the crashes for these subjects, but unable to provide bucketing, and more difficult to set up and more expensive (though still relatively cheap---it requires minutes for taming, vs. the seconds of SCB) than SCB.  When SCB applies, it is likely to be faster and more useful than mutant-based FPF ranking.  However, a user will obviously seldom know for certain that all faults in a set of crashes correlate to bug types that SCB supports. One approach would be to use SCB to bucket crashes, and then apply our approach to any remaining inputs, and examine the first few inputs in repair-FPF order.  In Section \ref{conc} we will return to this point.

### 2019-09-30 journal/introduction.tex
more on fuzzgoat and SCB

\begin{itemize}
\item generally expanding discussion of our approach, including the conceptual basis for using mutants to measure similarity of executions, and related work,
\item providing an extended example (in Section \ref{sec:example}) to help readers better understand the metric, FPF-based fuzzer taming, and our fault localization approach,
\item introducing and evaluating another compiler fault localization approach (in Section \ref{sec:covloc}), based on code coverage changes,
\item and including a much more in-depth examination of the computational costs of our approach and various ways of reducing that cost, including experimental evaluations (in Section \ref{sec:highcost}).
\end{itemize}

>>>>

\begin{itemize}
\item generally expanding discussion of our approach, including the conceptual basis for using mutants to measure similarity of executions, and related work,
\item providing an extended example (in Section \ref{sec:example}) to help readers better understand the metric, FPF-based fuzzer taming, and our fault localization approach,
\item introducing and evaluating another compiler fault localization approach (in Section \ref{sec:covloc}), based on code coverage changes,
\item including a much more in-depth examination of the computational costs of our approach and various ways of reducing that cost, including experimental evaluations (in Section \ref{sec:highcost}),
\item and showing how our approach works for fuzzer taming of non-compiler bugs, highlighting the limitations of both our technique and the state-of-the-art semantic crash bucketing (SCB) \cite{SCB} approach.
\end{itemize}
